Title of the document here

### 2015-01-23 rmtw/assignment_1/assignment_1.tex
Started writing intro

%------------------------------------------------------------------------- 
\Section{Introduction}

1. Statement of the problem
  Measuring the inherent readability of various programming languages. 
  \newline \newline
2. Existing literature
  No previous studies have compared the readability of different programming languages. There are however existing papers that explore the concept of readability. \cite{buse2010learning} talks about readability and presents a metric system to automatically measure readability. \cite{posnett2011simpler} build on \cite{buse2010learning}'s concept to provide a simpler and more accessible metric system. \cite{hansen2013makes} focus on what makes code hard to read and presents those factors. 
  \newline \newline
3. Why is it important?
\cite{aggarwal2002integrated} talks about code maintainability and mentions readability as a factor related to maintainability.

@@

\textbf{Industry}: To compare code of different language to be able to prioritize them. \\
\textbf{Academia}: To conduct more studies on the area which compare different languages. \\
To determine which languages are most suited for academic teaching. (When other attributes of programming languages are not constraints).

>>>>

%------------------------------------------------------------------------- 
\Section{Introduction}
Comparisons between programming languages are difficult to perform, due to characteristical differences between languages, such as syntax. One aspect of code is its readability, which in turn is a determining factor of a piece of software's quality and maintainability \cite{aggarwal2002integrated, elshoff1982improving}. Buse \& Westley define readability as ``a property that influences how easily a given piece of code can be read and understood'' \cite{buse2010learning}. Existing studies related to the concept of code readability focus on differences between specific languages, which can be seen in \cite{buse2010learning}. Buse \& Westley introduce a metrics system for measuring the readability of code, and Java is the language of choice in the study \cite{buse2010learning}. Buse \& Westley also discuss readability and its impact on programming language design, but they do not explore the readability differences between languages \cite{buse2010learning}. Posnett et al. \cite{posnett2011simpler} have further developed Buse \& Westley's metrics model to provide a simpler and more practical model which builds on size metrics as well as Halstead metrics \cite{halstead1977elements}.

2. Existing literature
  No previous studies have compared the readability of different programming languages. There are however existing papers that explore the concept of readability. \cite{buse2010learning} talks about readability and presents a metric system to automatically measure readability. \cite{posnett2011simpler} build on \cite{buse2010learning}'s concept to provide a simpler and more accessible metric system. \cite{hansen2013makes} focus on what makes code hard to read and presents those factors. 
 3. Why is it important?
\cite{aggarwal2002integrated} talks about code maintainability and mentions readability as a factor related to maintainability.

@@

\textbf{Industry}: To compare code of different language to be able to prioritize them. \\
Further studies can be conducted to see if there is a correlation between popularity of projects and the readability of the langauage(s) used in the project. \\
\textbf{Academia}: To conduct more studies on the area which compare different languages. \\
To determine which languages are most suited for academic teaching. (When other attributes of programming languages are not constraints).
